### 2016-07-09 paper/algorithms.tex
Text and section reorg

	$\epsilon_0=-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{MF_0})(\Lambda_0)+\mathcal M_{HF}(\Psi_{MF_0})-\mathcal M_{MF_0}(\Psi_{MF_0})$}
	\State{Calculate QoI $I(q_{MF_0},u_{MF_0})$}
	\While{$i<$ \texttt{maxIter} and $|\epsilon_i/I(q_{MF_i},u_{MF_i})|>$ \texttt{errTol}}
		\State{\begin{varwidth}[t]{\linewidth}Localize $\epsilon_i$ and use this decomposition to guide formation of new \par\hskip\algorithmicindent mixed-fidelity model MF$_{i+1}$\end{varwidth}}
		\State{$i\gets i+1$}
		\State{Solve for stationary point $\Psi_{MF_i}$ of augmented Lagrangian $\mathcal{M}_{MF_i}$}
		\State{Solve QoI error adjoint equation, linearized about $\Psi_{MF_i}$, for

@@

Algorithm~\ref{alg:refSeries} is applicable to a large class of models. The lower-fidelity model could, for example, be a simplified model including fewer physical phenomena, be a reduced-order model, or have a reduced parameter space. The two models could also correspond to two levels of mesh-refinement, though in this case the method described in~\cite{BecVex05} could be more efficient, since interpolation could be used to estimate $\Psi_{HF}-\Psi_{LF}$ instead. The derived error estimate is not applicable to all models, however. The two models have to be expressed in a weak form, so this cannot be applied to, for example, a model of chemical reactions using kinetic Monte Carlo. We need some degree of compatibility between the two models; namely, we assume that $\Psi_{LF}$ will be in a space admissible to $\mathcal{M}'_{HF,\Psi}$, and that the QoI functional $I$ is applicable to both $(q_{HF},u_{HF})$ and $(q_{LF},u_{LF})$.
% 
\subsection{Complexity Analysis}\label{sect:alg_complexity}
%
We now derive the computational complexity of using Algorithm~\ref{alg:refSeries} to solve an inference problem, and compare it to extant strategies. Let the state, adjoint, and parameter variables each have $N$ degrees of freedom, and assume that an `all at once' strategy is used to solve the KKT system. The cost of single linear solve with such a system is $\orderof{3N}^{\gamma}$, where $\gamma$ depends on the linear solver used~\cite{}. The cost of solving for the auxiliary variables, a linear system, is $\orderof{3N}^{\gamma}$. \red{The parts of the supplementary adjoint corresponding to the primary and auxiliary variables can be solved separately, and thus the cost of computing the supplementary adjoint is also $\orderof{3N}^{\gamma}$.}

>>>>

	$\epsilon_0=-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{MF_0})(\Lambda_0)+\mathcal M_{HF}(\Psi_{MF_0})-\mathcal M_{MF_0}(\Psi_{MF_0})$}
	\State{Calculate QoI $I(q_{MF_0},u_{MF_0})$}
	\While{$i<$ \texttt{maxIter} and $|\epsilon_i/I(q_{MF_i},u_{MF_i})|>$ \texttt{errTol}}
		\State{\begin{varwidth}[t]{\linewidth}Localize $\epsilon_i$ (see section~\ref{sect:error_est_localize}) and use this decomposition to guide formation of new \par\hskip\algorithmicindent mixed-fidelity model MF$_{i+1}$\end{varwidth}}
		\State{$i\gets i+1$}
		\State{Solve for stationary point $\Psi_{MF_i}$ of augmented Lagrangian $\mathcal{M}_{MF_i}$}
		\State{Solve QoI error adjoint equation, linearized about $\Psi_{MF_i}$, for

@@

Algorithm~\ref{alg:refSeries} is applicable to a large class of models. The lower-fidelity model could, for example, be a simplified model including fewer physical phenomena, be a reduced-order model, or have a reduced parameter space. The two models could also correspond to two levels of mesh-refinement, though in this case the method described in~\cite{BecVex05} could be more efficient, since interpolation could be used to estimate $\Psi_{HF}-\Psi_{LF}$ instead. The derived error estimate is not applicable to all models, however. The two models have to be expressed in a weak form, so this cannot be applied to, for example, a model of chemical reactions using kinetic Monte Carlo. We need some degree of compatibility between the two models; namely, we assume that $\Psi_{LF}$ will be in a space admissible to $\mathcal{M}'_{HF,\Psi}$, and that the QoI functional $I$ is applicable to both $(q_{HF},u_{HF})$ and $(q_{LF},u_{LF})$.
\subsubsection{Error Estimate Localization}\label{sect:error_est_localize}
%
Algorithm~\ref{alg:refSeries} does not require a specific method for localizing the error estimate. A na\"{i}ve approach would be to write the error estimate as a sum of integrals over elements and their boundaries, and calculate the error contribution by each element as the integral over that element. While simple, this method can lead to non-zero error contributions from elements in which the high-fidelity model is already being used, making the error decomposition more difficult to interpret and use for refinement.

We instead use the alternative method described in \cite{vanOpstaletal15}, decomposing the error estimate into contributions from locally supported basis functions rather than elements. For convenience of notation in this section, we drop subscripts so that $\Psi=\Psi_{LF}$, $Q=Q_{HF}$, and $U=U_{HF}$; for our numerical experiments, we have $Q_{LF}\subseteq Q$ and $U_{LF}=U$. Note that the error estimate in Equation \ref{eq:finErrExp} can be equivalently written as,
%
\begin{equation}
I(q_{HF},u_{HF})-I(q_{LF},u_{LF})=-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi)(\Lambda)+\mathcal{L}'_{HF,\xi}(\xi_\Psi)(\chi_\Psi)+\mathcal{R}(e^3). \nonumber
\end{equation}
%
We consider a finite-dimensional \red{conforming} subspace $(Q^h\times U^h\times U^h)^3 \subset (Q\times U\times U)^3$ which contains the approximations $(\Lambda^h,\chi_\Psi^h)$. Define a basis $\Phi^h=\{(\varphi,\upvarphi)_i\}_{i\in I}$ consisting of locally supported functions such that span $\Phi^h=(Q^h\times U^h\times U^h)^3$; we can then write $(\Lambda^h,\chi_\Psi^h)=(\sum\limits_{i\in I}\varphi_i\lambda_i,\sum\limits_{i\in I}\upvarphi_i \chi_i)$. The error estimate,
%
\begin{equation}
\epsilon = -\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi)(\Lambda)+\mathcal{L}'_{HF,\xi}(\xi_\Psi)(\chi_\Psi) \leq \sum_{i\in I} \varepsilon_i,
\end{equation}
%
where,
%
\begin{equation}\label{eq:basisblame}
\varepsilon_i = \left| -\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi)(\lambda_i\varphi_i)+\mathcal{L}'_{HF,\xi}(\xi_\Psi)(x_i\upvarphi_i) \right|
\end{equation}
%
can be interpreted as the error contribution from the basis function $(\varphi,\upvarphi)_i$. Near the interfaces between the low-fidelity and high-fidelity regions, basis functions may have their support divided between the two regions and thus have a nonzero error contribution. The basis functions with the largest error contributions are flagged, and the elements in their support are refined.  
% 
\subsection{Complexity Analysis}\label{sect:alg_complexity}
%
We now derive the computational complexity of using Algorithm~\ref{alg:refSeries} to solve an inference problem, and compare it to extant strategies. Let the state, adjoint, and parameter variables each have $N$ degrees of freedom, and assume that an `all at once' strategy is used to solve the KKT system. The cost of single linear solve with such a system is $\orderof{3N}^{\gamma}$, where $\gamma$ depends on the linear solver used~\cite{}. The cost of solving for the auxiliary variables, a linear system, is $\orderof{3N}^{\gamma}$. \red{The parts of the supplementary adjoint corresponding to the primary and auxiliary variables can be solved separately, and thus the cost of computing the supplementary adjoint is also $\orderof{3N}^{\gamma}$.}
